\documentclass[11pt,a4paper,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{lipsum}
\usepackage{setspace}
\usepackage[margin=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{colorlinks=true,
            linkcolor=blue,
            citecolor=black,
            urlcolor =blue}
\usepackage{enumitem}
%\setlist{nolistsep}
\setlist{parsep=0pt}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage{tabularx}

\fancyhf{}
\fancyhead[L]{Curriculum Vitae: Amir Neto}
\fancyhead[R]{\thepage}
\pagestyle{fancy}
\thispagestyle{plain}

\setlength\parskip{0pt}

\titleformat{\section}
  {\bfseries}{}{0em}{}[\hrule height 0.2pt]
\titlespacing*{\section}
  {0pt}{15pt}{10pt}


\begin{document}
\begin{center}
  \Large{\textbf{Amir Borges Ferreira Neto}} \\
\end{center}

\noindent
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\begin{tabularx}{\textwidth}{lR}
Department of Economics           & \emph{Updated: \today}  \\
College of Business and Economics & \href{mailto: Your email}{amneto@mix.wvu.edu} \\
West Virginia University          & \href{http:// Your web address}{www.amirneto.com}\\
1601 University Ave., PO Box 6025 & Skype: amirneto\\
Morgantown, WV, 26505  & +1(304)276.0726\\
\end{tabularx}

\section{RESEARCH INTEREST}
\begin{itemize}[label={}]
  \item \emph{Primary:} Urban \& Regional Economics and Public Economics
  \item \emph{Secondary:} Urban Amenities, Cultural Activities, Energy, and Labor
\end{itemize}

\section{EDUCATION}
\noindent
\begin{tabularx}{\textwidth}{lR}
\emph{West Virginia University} & \emph{Morgantown, WV} \\
$\qquad$Ph.D. in Economics              & 2019 (expected) \\
\\
\emph{Universidade Federal de Juiz de Fora} & \emph{Juiz de Fora, Brazil} \\
$\qquad$M.A. in Applied Economics     & 2012 \\
$\qquad$B.A. Economics     & 2009 \\
\end{tabularx}

\section{JOURNAL ARTICLES}
\begin{enumerate}
  \item Randall Jackson, P\'eter J\'arosi, Amir B. Ferreira Neto and Elham Erfanian, ``Woody Biomass Processing and Rural Regional Development'' \emph{Economics Development Quarterly}, forthcoming.
  \item Amir B. Ferreira Neto and Joshua Hall, ``Economies of Scale and Governance of Library Systems: Evidence from West Virginia'', \emph{Economics of Governance}, 2018: https://doi.org/10.1007/s10101-018-0215-2.
  \item Amir B. Ferreira Neto, Amanda Ross and Adam Nowak, ``Do Tourists Tip More than Local Consumers? Evidence of Taxi Rides in New York City'',  \emph{International Regional Science Review}, 2018: https://doi.org/10.1177/0160017618798431.
  \item Amir B. Ferreira Neto and Joshua Hall, ``The Effect of Health Care Entrepreneurship on Local Health: The Case of MedExpress in Appalachia'' \emph{Journal of Regional Analysis and Policy}, v. 48, n. 2, p. 23--31.
  \item Amir B. Ferreira Neto, Fernando S. Perobelli, and Alexandre Rabelo, ``Looking Behind the Scenes: An Assessment of the Interdependence of Brazilian Cultural Industries'' \emph{The Review of Regional Studies}, v.48, 2018, p.217–-243.
  \item Joshua Hall, Josh Matti and Amir B. Ferreira Neto, ``Rent-Seeking in the Classroom and Textbooks: Where are we after 50 Years?'' \emph{Public Choice}, 2018: https://doi.org/10.1007/s11127-018-0563-z.
  \item Amir B. Ferreira Neto, ``Charity and Public Libraries: Does Government Funding Crowd out Donations?'' \emph{Journal of Cultural Economics}, 2018: https://doi.org/10.1007/s10824-018-9318-4.
  \item  Randall Jackson, Amir B. Ferreira Neto, and Elham Erfanian, ``Woody Biomass Processing: Potential Economic Impacts on Rural Regions'' \emph{Energy Policy}, v.115, 2018, p.66--77.
  \item Elham Erfanian and Amir B. Ferreira Neto, ``Scientific Output: Labor or Capital Intensive? An analysis for selected countries.'' \emph{Scientometrics}, v.112, n.1, 2017, p.461--482.
  \item Amir B. Ferreira Neto,, Collin Hodges and Hyunwoong Pyun, ``Voting Dynamics and the Birth of State-owned Casinos in Kansas.'' \emph{Economics Bulletin}, v.36, n.1., 2016.
  \item Eduardo Gon\c{c}alves and Amir B. Ferreira Neto, ``Intersectoral Flows of Technological Knowledge in Emerging Countries: An Input-Output Analysis.'' \emph{Cepal Review}, v.118, 2016.
  \item Amir B. Ferreira Neto, Wilson Corr\^ea and Fernando Perobelli, ``Consumo de Energia e Crescimento Econ\^omico: Uma An\'alise para o Brasil'' 1970-2009. \emph{An\'alise Econ\^omica}, v.34, 2016, p.181--204.
  \item Amir B. Ferreira Neto, Fernando Perobelli and Suzana Bastos, ``Comparing Energy Use Structures: An Input-Output Decomposition Analysis of Large Economies.'' \emph{Energy Economics}, v. 43, 2014, p. 102--113.
  \item Amir B. Ferreira Neto, ``Converg\^encia de Renda e Converg\^encia de Consumo de Energia El\'etrica: Uma An\'alise Comparativa.'' \emph{Revista Brasileira de Estudos Regionais e Urbanos} v.08, n. 2, 2014, p. 123--138.
  \item Amir B. Ferreira Neto and Fernando Perobelli, ``Spatial Analysis of Cultural Activities in the Microregions of Minas Gerais.'' \emph{EconomiA}, v.14, 2013, p.139--157.
  \item Amir B. Ferreira Neto, Ricardo Freguglia and Bernardo Fajardo, ``Evid\^encias de Diferenciais Salariais para o Setor Cultural e Ocupa\c{c}\~oes Art\'isticas no Brasil.'' \emph{Economia Aplicada}, v.16, n.1, 2012, p.49--76
  \item Eduardo Haddad, Amir B. Ferreira Neto, and Fernando Perobelli, ``Fragmenta\c{c}\~ao Geopol\'itica: Uma An\'alise Estrutural das Propostas de Separatismo no Brasil.'' \emph{Economia Aplicada}, v.16, n.4, 2012, p.531--566.
\end{enumerate}

\section{UNDER REVIEW}
\begin{enumerate}
  \item Jamie Bologna Pavlik and Amir B. Ferreira Neto, ``Does Corruption Impact the Informal-Formal Sector Wage Gap? Evidence from Brazil''
  \item Eduardo Minuci, Amir B. Ferreira Neto, and Joshua Hall, ``Efficiency, but at what Cost? Evidence from a DEA Analysis of WV School Districts''
\end{enumerate}

\section{WORKING PAPERS}
\begin{enumerate}
  \item Amir B. Ferreira Neto, ``Do Public Libraries Impact Local Labor Markets? Evidence from Appalachia'' (Job Market Paper)
  \item Amir B. Ferreira Neto, ``The Diffusion of Cultural District Laws Across {US} States''
  \item Ricardo Freguglia and Amir B. Ferreira Neto, ``How Much does Talent Matter? Evidence from the Brazilian Formal Cultural Industry''
  \item In\'acio Ara\'ujo, Randall Jackson, Amir B. Ferreira Neto, and Fernando S. Perobelli, ``Environmental Costs of European Union Membership: A Structural Decomposition Analysis''
  \item Luiz Carlos Ribeiro, Thiago Rios and Amir B. Ferreira Neto ``Spatial Spillovers of the Cultural Employment Growth in Brazilian Municipalities''
  \item Brad Humphreys and Amir B. Ferreira Neto, ``Localization Economies and Firm Productivity: Evidence from Football Teams in S\~ao Paulo, Brazil''
%  \item Jamie Bologna Pavlik, Amir B. Ferreira Neto and Ricardo Freguglia, ``How Does Corruption Affect Labor Supply? An Analysis of Reallocation.''
%  \item Amir B. Ferreira Neto and Adam Nowak, ``a''
\end{enumerate}

\section{OTHER SELECTED PUBLICATIONS}
\begin{enumerate}
  \item Amir B. Ferreira Neto, Review of Lessons from the Economics of Crime: What Reduces Offending? by Cook, Machin, Marie, \& Mastrobuoni (Eds.) \emph{The Review of Regional Studies}, v.45, n.3, 2015  p.285-293.
  \item Amir B. Ferreira Neto, and Randall Jackson, ``MATLAB and Python Functions for Weighted Disaggregation.'' RRI TechDoc 2015--02.
  \item Amir B. Ferreira Neto, ``Setting up a SAM in Excel Using VBA.'' RRI TechDoc 2014--05.
  \item Amir B. Ferreira Neto, ``Using a Spreadsheet SAM for GAMS CGE Modeling.'' RRI TechDoc 2014--04.
  \item Amir B. Ferreira Neto, and Randall Jackson, ``Social Accounts for CGE in a Multi-Software Environment: Implan, GAMS and Excel.'' RRI ResourceDoc 2014--03.
  \item Rodrigo Zeidan, Afonso Cozzi, Solange Leonel and Amir B. Ferreira Neto, ``Obst\'aculos \`a Participa\c{c}\~ao de Pequenas e M\'edias Empresas no Mercado de Capitais'', in: IBGC. (Org.). \emph{O Futuro da Governan\c{c}a Corporativa -- Desafio e Novas Fronteiras}, 2013, p. 247--262.
\end{enumerate}

\section{RELEVANT PROFESSIONAL EXPERIENCE}
\noindent \textbf{West Virginia University}:
\begin{itemize}[align=left]
  \item[2017--Present] \emph{Instructor of Record, Department of Economics}
  \begin{itemize}
    \item[] Principles of Microeconomics: Summer 2017, Spring 2018, Summer 2018
    \item[] Survey of Economics: Fall 2017
  \end{itemize}

  \item[2016--2017] \emph{Teaching Assistant, Department of Economics}
  \begin{itemize}
    \item[] Principles of Microeconomics, Principles of Macroeconomics
  \end{itemize}

	\item[2014--2016] \emph{Graduate Research Assistant, Regional Research Institute}
\end{itemize}

\noindent \textbf{Funda\c{c}\~ao Dom Cabral}:
\begin{itemize}[align=left]
  \item[2012--2014] \emph{Junior Researcher}
\end{itemize}

\noindent \textbf{Universidade Federal de Juiz de Fora}:
\begin{itemize}[align=left]
  \item[2011--2011] \emph{Teaching Assistant, Department of Economics}
  \begin{itemize}
    \item[] Graduate Microeconomics II (Applied Game Theory)
  \end{itemize}
\end{itemize}

\noindent \textbf{Referee}:\\
 \emph{Cepal Review, Contemporary Economic Policy, Economic Systems Research, Energy Efficiency, Energy Economics, Energy Strategy Reviews, Environmental Economics and Policy Studies, Huella Econ\'omica, Journal of Entrepreneurship  and Public Policy, Nova Economia, Papers in Regional Science, Pesquisa e Planejamento Econ\^omico, Revista Brasileira de Estudos Regionais e Urbanos, Revista Semestre Economico, Space and Culture, The Review of Regional Studies}


\section{AWARDS AND HONORS}
\begin{itemize}[align=left]
  \item[2017] Jon Vilasuso Advanced Doctoral Student Award, West Virginia University
  \item[2017] Co-Winner of the Best Graduate Student Paper in Economics at the 54th AEF Conference
  \item[2016] W. Marston and Katharine B. Becker Doctoral Fellowship
  \item[2010--2012] CNPq Fellowship and FAPEMIG Scholarship for Masters studies
\end{itemize}

\section{AFFILIATIONS}
American Economic Association, Western Economic Association, Southern Economic Association, Regional Science International Association, North American Regional Science Association, Southern Regional Science Association, Urban Economic Association

%\section{REFERENCES}
%\noindent
%\begin{tabular}{lll}
%Joshua C. Hall & Brad Humphreys  &  Amanda Ross \\
%\emph{Advisor} & & \\
%Professor & Professor &  Assistant Professor\\
%West Virginia University & West Virginia University & University of Alabama \\
%joshua.hall@mail.wvu.edu & brad.humphreys@mail.wvu.edu &  ross@culverhouse.ua.edu  \\
%304-293-7870 & 304-293-4092 &  205-348-6313 \\
% & & \\
%Randall Jackson & &\\
% Director& & \\
%  Regional Research Institute & & \\
%  randall.jackson@mail.wvu.edu  & &\\
% 304-293-8734& & \\
%\end{tabular}
%-----------------------------------------
\end{document}
